Estimating duration using survival analysis

### 2024-07-29 cis-perfect-testing.tex
Chrstil comment on vague v weakly informative prior
Christl comment on Beta(0.5, 0.5) being uninformative

Uninformative Beta priors on the hazard are problematic in this context.
An uninformative prior would be of the form $\lambda_t \dist \BetaDist(\alpha, \alpha)$.
Commonly, $\alpha$ is chosen to be $0.5$ (Jeffreys' Prior) or $1$ (a uniform prior).
Even though these priors are uninformative on the hazard, they become highly informative on the survival. 
Specifically, they tend to favour shorter survival times (see \cref{perf-test:fig:flat-prior}).
An intuitive explanation of this follows from the fact that priors of this form have an expected value of 0.5.
The expected survival time, $\E \left( \prod_{i=1}^{t-1} (1-\lambda_t) \right)$, is therefore equal to $0.5^{t-1}$, a quantity that declines rapidly.
This prior expresses extreme scepticism in estimates from previous studies, such as \cref{E-ATACCC} and the meta-analysis of \textcite{cevikShedding}.
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/flat-prior}
  \caption[Uninformative priors for the hazard]{
    (A) Density of Beta(1, 1) flat prior and Beta(0.5, 0.5) uninformative priors.
    (B) Prior predictive survival time (mean and 95\% CrI).
    The implied prior on the survival time is short when using either prior on the hazard at each time.
  }
 \label{perf-test:fig:flat-prior}
\end{figure}

Instead, I propose a weakly informative (or vague) prior Beta(0.1, 1.9), which has mean 0.05 and minimal information.
The amount of information in a Beta distribution is related to the sum of its parameters.
Here, the sum equals 2, the same as the flat prior case.
The central 95\% probability mass of Beta(0.1, 1.9) is 0.00--0.47.
The central estimate, of 0.05, is in line with previous estimates that the median duration in the range 15--20 days~\autocite{cevikShedding}.
This prior gives a very vague prior predictive distribution on the survival time (see \cref{perf-test:fig:vague-prior}).
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/vague-prior}
  \caption[Vague prior for the hazard]{
    (A) Density of Beta(0.1, 1.9) vague prior.
    (B) Prior predictive survival time (mean and 95\% CrI).
    Note the different x-axis to \cref{perf-test:fig:flat-prior}.
  }
  \label{perf-test:fig:vague-prior}
\end{figure}

>>>>

Uninformative Beta priors on the hazard are problematic in this context.
An uninformative prior would be of the form $\lambda_t \dist \BetaDist(\alpha, \alpha)$.
Commonly, $\alpha$ is chosen to be $0.5$ or $1$ (a uniform prior).
The former, $\alpha = 0.5$, is Jefferys’ prior~\autocite{jeffreysInvariant}, commonly considered an uninformative prior because it is invariant to parameterization~\autocite[53]{gelmanBDA}.
Even though these priors are uninformative on the hazard, they become highly informative on the survival. 
Specifically, they tend to favour shorter survival times (see \cref{perf-test:fig:flat-prior}).
An intuitive explanation of this follows from the fact that priors of this form have an expected value of 0.5.
The expected survival time, $\E \left( \prod_{i=1}^{t-1} (1-\lambda_t) \right)$, is therefore equal to $0.5^{t-1}$, a quantity that declines rapidly.
This prior expresses extreme scepticism in estimates from previous studies, such as \cref{E-ATACCC} and the meta-analysis of \textcite{cevikShedding}.
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/flat-prior}
  \caption[Uninformative priors for the hazard]{
    (A) Density of Beta(1, 1) flat prior and Beta(0.5, 0.5) uninformative priors.
    (B) Prior predictive survival time (mean and 95\% CrI).
    The implied prior on the survival time is short when using either prior on the hazard at each time.
  }
 \label{perf-test:fig:flat-prior}
\end{figure}

Instead, I propose the vague prior Beta(0.1, 1.9), which has mean 0.05 and minimal information.
The amount of information in a Beta distribution is related to the sum of its parameters.
Here, the sum equals 2, the same as the flat prior case.
The central 95\% probability mass of Beta(0.1, 1.9) is 0.00--0.47.
The central estimate, of 0.05, is in line with previous estimates that the median duration in the range 15--20 days~\autocite{cevikShedding}.
This prior gives a very vague prior predictive distribution on the survival time (see \cref{perf-test:fig:vague-prior}).
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/vague-prior}
  \caption[Vague prior for the hazard]{
    (A) Density of Beta(0.1, 1.9) vague prior.
    (B) Prior predictive survival time (mean and 95\% CrI).
    Note the different x-axis to \cref{perf-test:fig:flat-prior}.
  }
  \label{perf-test:fig:vague-prior}
\end{figure}
